\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

% Font options
\usepackage[sfdefault]{roboto}  % Sans-serif font

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

% Ensure PDF is machine readable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge Goutham R} \\[2ex]

  \small 
  \faMobile \hspace{.5pt}  \href{tel:9113064916}{+91 9113064916} 
  $|$ 
  \faAt \hspace{.5pt} \href{mailto:goutham67r@gmail.com}{goutham67r@gmail.com} 
  $|$ 
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/goutham-ramesh-982220192/}{linkedin.com/in/goutham-ramesh-982220192} 
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/G0uth4m}{github.com/G0uth4m}
\end{center}


\section{Education}
\resumeSubHeadingList
  \resumeSubheading
      {PES University}{Bengaluru, Karnataka}
      {B.Tech in Computer Science}{June 2017 -- May 2021} \newline
      \resumeSubHeadingList
        \resumeItem{\textbullet\ \textbf{GPA:} {8.78/10}.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd


\section{Experience}
\resumeSubHeadingList
  \resumeSubheading
  {Coinbase}{Mar 2025 -- Present}
  {Software Engineer}{Bengaluru, Karnataka} \newline
  \resumeSubHeadingList
      \resumeItem{\textbullet\ Engineered an automated gRPC diff testing framework to validate APIs between staging and production environments, proactively catching over \textbf{531} breaking changes and reducing production incidents by \textbf{30\%} across Coinbase in 2025.}
      \resumeItem{\textbullet\ Developed a QA AI agent which reduced \textbf{40\%} cost spent on external QA service providers.}
  \resumeSubHeadingListEnd
  \resumeSubheading
      {Walmart Global Tech India}{Jul 2021 -- Mar 2025}
      {Software Engineer 3}{Bengaluru, Karnataka} \newline
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Designed an End-to-End Ordering System for Walmart Store Remodels, achieving cost savings of approximately \textbf{\$27M} annually for international operations.}
          \resumeItem{\textbullet\ Built a generic search framework to search by any column on any table in MSSQL Server.}
          \resumeItem{\textbullet\ Implemented Auto Secret Rotation for MSSQL servers, saving \textbf{15 days} of manual effort per team annually.}
          \resumeItem{\textbullet\ Reduced approximately \textbf{10 minutes} of downtime per microservice annually by eliminating the need for application restarts during configuration and secret changes, ensuring continuous service availability.}
          \resumeItem{\textbullet\ Received Annual Excellence Award twice (2022 and 2025) for mentoring engineers and significant contributions to customers.}
      \resumeSubHeadingListEnd
  \resumeSubheading
      {Walmart Global Tech India}{Jan 2021 -- Jun 2021}
      {Software Engineer Intern}{Bengaluru, Karnataka} \newline
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Developed and optimized Apache Spark jobs for large-scale data processing on Google Cloud Dataproc clusters.}
          \resumeItem{\textbullet\ Collaborated with distributed cross-functional teams to implement ETL workflows for business-critical analytics.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd


\section{Projects}
\resumeSubHeadingList

  \resumeSubheading
      {AI Daily Stock Analyzer}{Sep 2025 -- Nov 2025} 
      {Automated Market Research Pipeline $|$ \emph{\faGithub \hspace{.5pt} \href{https://github.com/G0uth4m/news-api}{\color{blue}GitHub}}}{Python, LLMs, RSS, HTML} \newline
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Engineered a daily automated pipeline to iterate through listed Indian market stocks, fetching the latest 10 news articles per stock from various RSS feeds.}
          \resumeItem{\textbullet\ Integrated an LLM to process textual news data and assign a quantified buy rating (out of 10), augmented with stock-specific technical indicators.}
          \resumeItem{\textbullet\ Built a reporting module to generate a comprehensive HTML summary report, distributed seamlessly via automated daily morning emails.}
      \resumeSubHeadingListEnd
      \resumeSubheading
      {Rideshare - DBaaS}{Mar 2020 -- May 2020}
      {Database as a Service $|$ \emph{\faGithub \hspace{.5pt} \href{https://github.com/G0uth4m/Rideshare-with-DBaaS}{\color{blue}GitHub}}}{Python, Docker, Postgres} \newline
      \resumeSubHeadingList
          \resumeItem{\textbullet\ Designed and implemented a scalable, highly available Database as a Service (DBaaS) model for a Rideshare application.}
          \resumeItem{\textbullet\ Built two microservices: Users Service and Rides Service to manage respective data.}
          \resumeItem{\textbullet\ Utilized Docker for containerization and deployment, RabbitMQ for messaging, and Zookeeper for distributed coordination.}
      \resumeSubHeadingListEnd
\resumeSubHeadingListEnd


\section{Technical Skills}
\resumeSubHeadingList
  \resumeItem{\textbf{Programming Languages}: Java, C/C++, Golang, Python, JavaScript, SQL}
  \resumeItem{\textbf{Technologies}: Spring Boot, Azure SQL, Kubernetes, AWS, GCP, Docker, Kafka, Elasticsearch, Apache Spark}
  \resumeItem{\textbf{Development Tools}: Git, Jenkins, Cursor, Claude Code, Agile}
\resumeSubHeadingListEnd

\end{document}